Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/appendix.tex
Wordsmithing text in Appendix.

Here we include some additional examples of our splitting algorithm.

\crem{pending Nico}

@@

In \ref{sec:exampleQS}, we suggested that staged quickselect could be applied to one list and many queries.
In this example, we implement that behavior by passing \texttt{qs} to a higher order function.
Such a combinator, which operates over both stages at once, is possible because of the generality of \lang's abstractions.

Note that we have to define a datatype for integer lists at the second stage, which is given by \texttt{list2}.
\begin{lstlisting} 
1`atsignnext{`2`
  datatype list2 = Empty2 | Cons2 of int * list2
`1`}

>>>>

This appendix includes additional examples of the behavior of our
splitting algorithm.

@@

In \ref{sec:exampleQS}, we showed the output of splitting quickselect
applied to one list and $m$ queries.  Here, we generalize to mapping
quickselect onto a list of queries. Note that we have to define a
datatype for integer lists at the second stage, which is given by
\texttt{list2}.
\begin{lstlisting} 
1`atsignnext{`2`
  datatype list2 = Empty2 | Cons2 of int * list2
`1`}
